---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
echo = true

## Loading and preprocessing the data
```{r}
activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date)
processedActivity <- aggregate(steps ~ date, data = activity, sum)
hist(processedActivity$steps)
```
## Instructions
## 1. Calculate the total number of steps taken per day.
## 2. Make a histogram of the total number of steps taken each day.
## 3. Calculate and report the mean and median of the total number of steps taken per day.

## What is mean total number of steps taken per day?

```{r}
mean(processedActivity$steps)
```
## result: 10766.19
## What is the average daily activity pattern?
```{r}
mean(processedActivity$steps)
```
## result 10765

## Are there differences in activity patterns between weekdays and weekends?
## show a histogram of weekends
```{r}
weekendFactors <- grep ("S", weekdays(processedActivity$date))
weekdayFactors <- grep ("[MTWF]", weekdays(processedActivity$date))
hist(processedActivity[weekendFactors, "steps"])
hist(processedActivity[weekdayFactors, "steps"])
```
## Write figures to files
```{r}
png(file ="figure/plot1.png")
hist(processedActivity[weekendFactors, "steps"])
dev.off()
```
## show a histogram of weekdays